### 2015-05-14 paper.tex
uhhh yeah so we don't need opt great

In this stage, we continually select candidates of $k$ components from $Q$.  For each component, we choose the point that is the best possible center $c_i$ for that component and all points within $2r$ of that component.  Then, we assign all points to the nearest cluster center $c_i$.  Eventually, one of these subsets of components should give us a clustering with value at most $(1 + \epsilon) OPT$ (assuming $OPT$ is known; we will prove this).

@@

TODO: dscribe how we assume OPT is known and why that's valid.

@@

The algorithm, taken directly from \cite{firstpaper} is: *algorithm, I'll format it like you do*

>>>>

In this stage, we continually select candidates of $k$ components from $Q$.  For each component, we choose the point that is the best possible center $c_i$ for that component and all points within $2r$ of that component.  Then, we assign all points to the nearest cluster center $c_i$.  Eventually, one of these subsets of components should give us a clustering with value at most $(1 + \epsilon) OPT$, assuming OPT is known. While the algorithm could be shown to work using common estimators for OPT, they will be excluded from analysis.

@@

@@

\ref{alg:cluster2} taken directly from \cite{firstpaper} uses such a threshold graph to generate the clusters.
